---
title: "My Fancy Presentation"
author: "Monica Maria Solorzano Rodriguez"
date: "11/16/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My New Slide
Some content... two pound signs for a new slide

***
A slide without a title set with three asterisks 

## My Title

### Top Level Subheading

#### Second Level Subheading   

- Bullet one
- Bullet two

1. Item a
2. Item b  

Plain text  

*italicized text*   

**Bold text**   

`for (i %in% 1:10)`  

## Code Slide
Only result appears because in options echo is set to FALSE.
```{r}
head(mtcars, 2)
```

Eliminate the comment character and add code.
```{r, comment="", echo=TRUE}
head(mtcars, 2)
```

Code that isn't evaluated.
```{r, comment="", echo=TRUE, eval=FALSE}
head(mtcars)
```

## Plot Slide

```{r, comment="", echo=TRUE}
plot(mtcars$wt, mtcars$mpg, xlab= "Weight", ylab= "MPG")
```

## Another Plot Slide (centered + captions)

```{r, echo= FALSE, fig.align= 'center', fig.cap= "My Awesome figure"}
plot(mtcars$wt, mtcars$mpg, xlab= "Weight", ylab= "MPG")
```


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

